Fast Algorithms for Intersection of Non-matching Grids Using \plucker Coordinates.

### 2016-10-02 paper_intersections.tex
Hopefully final improvement to prolongation scheme.
Some improvements in 2d2d section.

%
\begin{figure}[!htb]
%   \vspace{0pt}
  \centering    
    \includegraphics[width=\textwidth]{\figpath prolongation_scheme_ip_jb_fix_italic.pdf}
  \caption{Advancing front algorithm for 1d-2d and 2d-3d intersections.}
  \label{fig:prolongation}
\end{figure}

@@

\subsection{Intersections Between Component Meshes}
\label{sec:components}
We consider here the situation that components are in the interior of the 3d bulk mesh. After we compute
all component-bulk intersections, we use it to easily find all the component-component intersection candidates.
If the bulk element intersects more than one component element, than we can create candidates from these.

Let us start with description of how we store the intersection results, which will be of great importance here.
For each element intersection, we save the following data: reference to component and bulk element, 
barycentric coordinates on both and index of the component. These objects are stored in separate vectors for each pair 
of dimensions. Further we define a sparse matrix (\emph{intersection map}) which has as many rows as there are elements in the mesh.
At each row (element), we save the references to all other elements, having intersection with element corresponding to this row, 
and references to the actual intersection data.

The algorithm for 2d-2d intersections works as follows. We iterate over all 2d-3d intersections, respectively over
the bulk elements having some intersections with 2d components. We look at the intersection map at the
bulk element row and collect all elements that have 2d-3d intersection with it.
Now comes in play the component number $\gamma$. If $\gamma$ is equal for both component elements, then 
these are part of a single continuous component and we do not compute any intersection.
Otherwise we obtain a new candidate pair, for which IP can be computed.

>>>>

%
\begin{figure}[!htb]
%   \vspace{0pt}
  \centering    
    \includegraphics[width=\textwidth]{\figpath prolongation_scheme_ip_pe_final.pdf}
  \caption{Advancing front algorithm for 1d-2d and 2d-3d intersections.}
  \label{fig:prolongation}
\end{figure}

@@

\subsection{Intersections Between Component Meshes}
\label{sec:components}
We consider here the situation where components are in the interior of the 3d bulk mesh. After we compute
all component-bulk intersections, we use it to easily find all the component-component intersection candidate
pairs.
If the bulk element intersects more than one component element, then we look for candidate pairs only among these.

Let us start with the description of how we store the intersection results, which will be of great importance here.
For each element intersection, we save the following data: references to the component and bulk element, 
the barycentric coordinates on both and the index of the component. These objects are stored in separate vectors for each pair of dimensions. Further we define a matrix (\emph{intersection map}) which has as many rows as there are elements in the mesh.
At each row, we save the references to all other elements, having intersection with the element corresponding to this row, and references to the actual intersection data.

The algorithm for 2d-2d intersections works as follows. We iterate over all 2d-3d intersections, in fact over
the bulk elements having some intersections with 2d components. We look at the intersection map at the
bulk element row and collect all elements that have 2d-3d intersection with it.
Then we create all possible pairs from the collected component elements.
Now comes in play the component number $\gamma$. If the elements of a single pair have $\gamma$ equal, then 
these are part of a single continuous component and we do not compute any intersection.
Otherwise we obtain a new candidate pair, for which IP can be computed.
